%!TEX root = ../main.tex

\section{Introduction}
\begin{frame}
	\frametitle{Table of Contents}
	\tableofcontents[currentsection,currentsubsection]
\end{frame}

\begin{frame}
	\frametitle{Setup I}
	\# \citet{Maguire2009}--Fig. 1

	\# vs.

	\# Pipeline industry trend
\end{frame}

\begin{frame}
	\frametitle{Setup II--\citet{Maguire2009} story}
	\begin{itemize}
		\item Existing model of a chemical.
			\subitem What it is, what it does
			\subitem Works well reg. prediction and control--it does exactly what it is supposed to
			\subitem Understanding of DDT public, stable and shared, too!
		\item Disruption!
		\item New model emerges
			\subitem Contradicts old model
			\subitem Valid in prediction and control
			\subitem Becomes public, stable and shared
		\item We have learned
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Setup III--Pipeline industry}
	\# Pipeline industry trajectories
\end{frame}

\blackgroup
\begin{frame}[plain]
	What's going on here?
	\note{
		\begin{itemize}
			\item What happened here?
			\item What is the difference between the two phenomena?
			\item Why did we get control over DDT but not oil spills?
		\end{itemize}
		}
\end{frame}
\egroup

\begin{frame}
\frametitle{Pipeline industry}
	\begin{block}{Examples}
		\begin{itemize}
			\item After every oil spill--never again--e.g., arctic oil spill, Kalamazoo
			\item Dedicated organization--NTSB
			\item Industry promoting notion of pipelines as safe
			\item Oil spilling into specific rivers--repeatedly
		\end{itemize}
	\end{block}
	\hrulefill

	So why did we take drastic action on DDT but not pipelines?

	\# Add Kalamazoo or burning river image
\end{frame}

\blackgroup
\begin{frame}[plain]
	\note{I am going to transition to learning now.}
\end{frame}
\egroup
